Higher-Order unification for free!

### 2024-04-15 paper/main.tex
attempt

\begin{proposition}[\wellb-enforcing]\label{prop:w-enforcing}
  Given two terms $s_1$ and $s_2$, if $\exists \rho, \rho s_1 \Eo \rho s_2$,
  then 
  $$
    \C{s_i}{t_i}{m_i}{l_i} ~\mathrm{for}~ i \in \{ 1,2 \} \Rightarrow
    t_1 \Ue t_2 \mapsto \sigma \label{prop:compilation-w}
  $$
\end{proposition}

\noindent
In other words the compiler outputs terms in \wellb, even if its
input is not.
Note that the property holds for any substitution, $\rho$ could be given by an
oracle and/or not necessarily be a most general one: in \wellb \Ue{} simply
does not contradict \Eo.

>>>>

\begin{proposition}[\wellb-enforcing]\label{prop:w-enforcing}
  Given a term $s$ in \Fo{}, 
  $$
    \C{s}{t}{m}{l} \Rightarrow \wellb(t)
  $$
\end{proposition}

\begin{proposition}[compiler-useful]\label{prop:w-noncontra}
  Given two terms $s_1$ and $s_2$, if $\exists \rho, \rho s_1 \Eo \rho s_2$,
  then 
  $$
    \C{s_i}{t_i}{m_i}{l_i} ~\mathrm{for}~ i \in \{ 1,2 \} \Rightarrow
    t_1 \Ue t_2 \mapsto \sigma \label{prop:compilation-w}
  $$
\end{proposition}

\noindent
In other words the compiler outputs terms in \wellb, even if its
input is not. And if two terms can unify in the source language
then these terms also unify in the target language. 
Note that the property holds for any substitution, $\rho$ could be given by an
oracle and/or not necessarily be a most general one: in \wellb \Ue{} simply
does not contradict \Eo. Also note that a compiler that
translate all terms to unification variables would satisfy this
property, but wound fail to verify \cref{prop:fidelity}.
